[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles

### 2020-08-17 paper/dcpo_gender_roles.Rmd
add cs plot

>>>>

```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, 2020 \\label{cs_2020}", fig.height=8, warning=FALSE}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_output.rda"))

theta_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "theta")

sigma_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "sigma")

p1_data <- theta_results %>%
    group_by(country) %>%
    top_n(1, year) %>%
    ungroup() %>%
    arrange(-mean) %>%
    mutate(half = ntile(mean, 2))

p1_data_a <- p1_data %>% filter(half==2) %>% mutate(ranked = as.factor(row_number(mean)))
p1_data_b <- p1_data %>% filter(half==1) %>% mutate(ranked = as.factor(row_number(mean)))

p1a <- ggplot(p1_data_a, aes(x = mean,
                             y = ranked)) +
    geom_segment(aes(x = `10%`, xend = `90%`,
                     y = ranked, yend = as.factor(ranked)),
                 na.rm = TRUE) +
    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
    theme_bw() + theme(legend.position="none",
                       axis.text.x  = element_text(size=8),
                       axis.text.y  = element_text(size=8),
                       axis.title.x = element_text(face="bold", size=8),
                       legend.text = element_text(size = 7),
                       legend.title = element_text(size=7, face = "bold"),
                       legend.key.size = unit(.5, "line"),
                       legend.background = element_rect(linetype = "solid",
                                                        color = "grey80",
                                                        size = .25),
                       legend.key = element_rect(colour = "white")) +
    scale_y_discrete(breaks = p1_data_a$ranked, labels=p1_data_a$country) +
    coord_cartesian(xlim=c(0, 1)) +
    labs(x = NULL, y = NULL)

p1b <- ggplot(p1_data_b, aes(x = mean,
                             y = ranked)) +
    geom_segment(aes(x = `10%`, xend = `90%`,
                     y = ranked, yend = ranked),
                 na.rm = TRUE) +
    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
    theme_bw() + theme(legend.position="none",
                       axis.text.x  = element_text(size=8),
                       axis.text.y  = element_text(size=8),
                       axis.title.x = element_text(face="bold", size=8)) +
    scale_y_discrete(breaks = p1_data_b$ranked, labels=p1_data_b$country) +
    coord_cartesian(xlim=c(0, 1)) +
    labs(x = NULL, y = NULL)

p1a + p1b

```
